---
title: "My awesome website"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---

Hi, my name is Jessie Li. I am a Biostatistics MS student in Columbia University. I am interested in genomics, public health and mental health issues. Check out about me for more information about me!

Here are some example codes for data science analysis. The dataset used in this 
```{r}
library(p8105.datasets)
library()
data("instacart")
```

The data that is ordered most frequently
```{r}
instacart |>
  group_by(aisle_id, order_number) |>
  summarize(sum = n()) |>
  ggplot(aes(x = aisle_id, sum)) +
  geom_point()
```

Orders per day (variety)
```{r}
instacart |>
  group_by(order_hour_of_day) |>
  summarize(ordered = n()) |>
  ggplot(aes(x = order_hour_of_day, y = ordered)) +
  geom_point() +
  geom_smooth()
```

Days since previous order vs Order Number Food vs Non-food
```{r}
instacart |>
  filter(!(department %in% c("household", "personal care", "pets", "babies", "bulk", "missing", "other"))) |>
  group_by(days_since_prior_order) |>
  summarize(total = n())|>
  ggplot(aes(x = days_since_prior_order, y = total)) +
  geom_point()
  
instacart |>
  filter(department %in% c("household", "personal care", "pets", "babies", "other")) |>
  group_by(days_since_prior_order) |>
  summarize(total = n())|>
  ggplot(aes(x = days_since_prior_order, y = total)) +
  geom_point()
```
People usually order every week/monthly. Weekly is more frequent than bi-weekly

added to cart order vs days since prior order
```{r}
instacart |>
  group_by(add_to_cart_order) |>
  summarize(days = mean(days_since_prior_order))|>
  ggplot(aes(x = add_to_cart_order, y = days)) +
  geom_point()
```
People tend to buy things they purchase frequently more early.





